\documentclass[line, margin]{res}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=magenta,      
    urlcolor=blue,
}

\setlength{\topmargin}{-0.4in}  % Start text higher on the page 
 \setlength{\oddsidemargin}{-0.4in}  % leftmargin of the page 
 \setlength{\evensidemargin}{-0.4in}  % right of the page 
  \setlength {\textwidth} {5.8in} %width of page

\begin{document}
	\thispagestyle{empty} % this page does not have a header
	\name{RAMA KRISHNA GONELLA}
	\address {\href {gvsriramakrishna@gmail.com} {gvsriramakrishna@gmail.com} \hspace{5ex}  Ph:+91.9642102244 	\hspace{5ex} \href{https://www.linkedin.com/in/ramakrishnagonella/}{LinkedIn}}
	

\begin{resume}

		\section{Profile}
		12 years of progressive experience in programming, analysis, design, consulting and product management roles.

		\section{Education}
			 {\bf University of Auckland Business School, New Zealand}
			 \newline Postgraduate Diploma in Commerce \& Business \textit { \hspace{3ex} June 2008 \-- October 2009}
			 
			{\bf Jawaharlal Nehru Technological University, India}
			 \newline Master of Computer Applications \textit{ \hspace{3ex} May 2003 \-- May 2006}
			
			{\bf Osmania University, India}
			\newline Bachelor of Science \textit{ \hspace{3ex} May 2000 \-- April 2003 }

		\section{Certifications}
					TOGAF 9.1 License: 125004 
					
					Pega Certified Systems Architect, Pega Business Architect, Pega Marketing Consultant (Chordiant Decisioning)
					
					Oracle Siebel CRM 8.1.1 Presales Specialist, Oracle Billing and Revenue Management Presales Specialist
		
		\section{Skills}
			{\bf Products \& Platforms}
			\begin{itemize}
			\item {\em Pega} \-– Unified CRM, Pega Marketing, Sales Automation, Configure\--Price\--Quote
			\item {\em Huawei BSS/OSS }\-– CRM, Convergent Billing System, Unified Product Catalog, Intelligent Networks
			\item {\em Oracle }\-–  Siebel CRM, Oracle Billing \& Revenue Management, Order \& Service Management
			\item {\em Convergys BSS/OSS }\-–  Geneva IRB Rating \& Billing, Dynamic Decisioning Solution, Order \& Revenue Management, Web Self-Service, Nokia Charge @ Once Intelligent platform
			\end{itemize}
			
						
			{\bf Network}
			\begin{itemize}
			\item	{\em Digitalk } \-- PaaS (Real-Time charging, Voice Routing, Margin Management)
			\end{itemize}
			
			{\bf  Programming Languages \& Technology}
			\begin{itemize}
			\item Java, C, PL/SQL, HTML, Python
			\item JSON, XML, SOA, Oracle Advanced Queues, Apache Kafka, NoSQL (MongoDB)
			\end{itemize}
			
			{\bf Industry Standards \& Frameworks}
			\begin{itemize}
			\item TMForum frameworks eTOM (Business process), SID (Information), TAM (Application) and TOGAF 9.1 EA
			\end{itemize}
		
	\section{Career Path}
	
	{\bf Associate Business Architect\-– Pega}  \hspace{5ex} {\em September 2014 – Till date}\\
	\begin{itemize}
		\item Sales support to various clientele and POCs design. After sales support including RFP and product capability assessment matrix.
		\item Ownership of product strategy, roadmap and design of Pega’s CRM SaaS suite (Decisioning, Customer Service \& Sales Automation).
		\item Using predictive and adaptive analytics in Pega to predict due actions for every interaction with customer.
		\item Idea to development of personalized journeys for acquisition, retention, negotiation, cross-sell and uplift modelling.
		\item UX conceptualization, design of wireframes and screen flows and development on Pega platform.
		\item Omni channel digital marketing campaigns, customer behavioral insights dashboards and Next-Best-Action strategies.
		\item Development of features such as strategy builder templates, customer lifetime value, investment budgets, churn calculations, smart-email conversations, sentiment analysis using 	Natural language processing (NLP).
		\item Created sales battle cards, market intelligence reports in CRM and BPM space.
		\item Feature design of smart conversation capabilities in chat-bot and intelligent virtual assistants.
		\item Sales support to clients – Euskaltel, Foxtel, Cox, Optus, Sprint, Telstra, Telecom Italia, Vodafone
	\end{itemize}
		
	{\bf Technology Project Lead \-– Huawei Technologies R\&D India}  \hspace{5ex} {\em March 2011 – September 2014}\\
	\begin{itemize}
		\item Contributed to RFP, RFQ, sales support, played key roles winning bids with aggregated worth of \$30 million apprx.
		\item Experience on Huawei BSS/OSS systems configurations, development, and E2E implementations.
		\item Created assets like product capability assessment, business strategy transformation planning and SWOT analysis.
		\item Hands on design experience on MACD Orders (Move, Add, Change, Disconnect), Lead to Cash, Order to Activate, Account Management, Service Management, Loyalty \& Campaign Management.
		\item Created solution architecture design for VIVA BSS/OSS wireless transformation project.
		\item Conducted IT systems health check and process due diligence for VIVA transformation project. 
		\item Developed MDM for wireless, wireline portfolio including customer master, accounts, billing data and data enrichment.
		\item Created solution and architecture document, interface specifications document, high-level design documents.
		\item Configuration of rating and billing plans (retail, wholesale), product catalogs, GL codes mapping and discounts.
		\item Delivered due-diligence analysis reports, pricing models analysis reports, product-modelling design, business requirements document (BRD), functional requirements specifications (FRS).
		\item E2E Implementations at Telcos – VIVA (Saudi Telecom Company), Togo Telecom, E-Plus Germany, Etisalat Dubai
		\end{itemize}

		
\end{resume}


\end{document}